This R markdown file can be used to visually assess the representation comparisons between Company and the talent pool

libraries
```{r}
library(dplyr)
library(ggplot2)
library(janitor)
library(tidyr)
```


## Comparing Company's Current Representation of Women and People of Color with the Representation seen in the Talent Pool

```{r}
load("../data/Comparison data/poc_comparison.rda")
poc_representation <- gather(poc_representation, key = "Department", value = representation, c(1:6)) %>% 
  filter(group == "both sexes") %>% 
  filter(area == "Baseline Representation" | area == "Current Representation") %>% 
  select(-1)
poc_representation$group <- "People of Color"

load("../data/Comparison data/women_comparison.rda")
women_representation <- gather(women_representation, key = "Department", value = representation, c(1:8)) %>% 
  filter(area == "Baseline Representation" | area == "Current Representation")
women_representation$group <- "Women"

compare <- bind_rows(women_representation, poc_representation)

compare$width <- ifelse(compare$area == "Baseline Representation", 0.7, 0.3)

plot <- compare %>% 
  ggplot() +
  geom_bar(aes(group, representation, fill = area),
           width = compare$width,
           position = "dodge",
           stat = "identity") + 
  facet_grid(~factor(Department, levels = c("Overall", "Engineering", "Marketing", "Sales", "Human Resources", "Legal", "APAC", "EMEA"))) +
  scale_fill_manual(values = c("#339966", "#33CCCC")) +
  xlab("Company Department") +
  ylab("Representation") + theme(axis.text.x = element_text(angle = 45)) +
  ggtitle("Comparing Company's Representation of Women and People of Color to Talent Pool") 

plot + geom_text(aes(x = group, y = representation, label = paste0(100 * round(representation, digits = 4), "%")), 
                 position = position_dodge(width = .5), vjust = .25)
```


## Comparing Company's Current Representation of Distinct Ethnic Groups with the Representation seen in the Talent Pool
```{r, echo = FALSE}
load("../data/Comparison data/ai_an_comparison.rda")
ai_an_representation <- gather(ai_an_representation, key = "Department", value = representation, c(1:6)) %>% 
  filter(group == "both sexes") %>% 
  filter(area == "Baseline Representation" | area == "Current Representation") %>% 
  select(-1)
ai_an_representation$group <- "American Indian"
ai_an_representation$width <- ifelse(ai_an_representation$area == "Baseline Representation", 0.7, 0.3)

plot <- ai_an_representation %>% 
  ggplot() +
  geom_bar(aes(Department, representation, fill = area),
           width = ai_an_representation$width,
           position = "dodge",
           stat = "identity") + 
  scale_fill_manual(values = c("#339966", "#33CCCC")) +
  xlab("Company Department") +
  ylab("Representation") + theme(axis.text.x = element_text(angle = 90)) +
  ggtitle("Comparing Company's Representation of American Indian or Alaskka Native to Talent Pool") 

plot + geom_text(aes(x = Department, y = representation, label = paste0(100 * round(representation, digits = 4), "%")), 
                 position = position_dodge(width = .5), vjust = .25)

load("../data/Comparison data/asian_comparison.rda")
asian_representation <- gather(asian_representation, key = "Department", value = representation, c(1:6)) %>% 
  filter(group == "both sexes") %>% 
  filter(area == "Baseline Representation" | area == "Current Representation") %>% 
  select(-1)
asian_representation$group <- "Asian"
asian_representation$width <- ifelse(asian_representation$area == "Baseline Representation", 0.7, 0.3)


plot <- asian_representation %>% 
  ggplot() +
  geom_bar(aes(Department, representation, fill = area),
           width = asian_representation$width,
           position = "dodge",
           stat = "identity") + 
  scale_fill_manual(values = c("#339966", "#33CCCC")) +
  xlab("Company Department") +
  ylab("Representation") + theme(axis.text.x = element_text(angle = 90)) +
  ggtitle("Comparing Company's Representation of Asian to Talent Pool") 

plot + geom_text(aes(x = Department, y = representation, label = paste0(100 * round(representation, digits = 4), "%")), 
                 position = position_dodge(width = .5), vjust = .25)


load("../data/Comparison data/black_comparison.rda")
black_representation <- gather(black_representation, key = "Department", value = representation, c(1:6)) %>% 
  filter(group == "both sexes") %>% 
  filter(area == "Baseline Representation" | area == "Current Representation") %>% 
  select(-1)
black_representation$group <- "Black"
black_representation$width <- ifelse(black_representation$area == "Baseline Representation", 0.7, 0.3)



plot <- black_representation %>% 
  ggplot() +
  geom_bar(aes(Department, representation, fill = area),
           width = black_representation$width,
           position = "dodge",
           stat = "identity") + 
  scale_fill_manual(values = c("#339966", "#33CCCC")) +
  xlab("Company Department") +
  ylab("Representation") + theme(axis.text.x = element_text(angle = 90)) +
  ggtitle("Comparing Company's Representation of Black to Talent Pool") 

plot + geom_text(aes(x = Department, y = representation, label = paste0(100 * round(representation, digits = 4), "%")), 
                 position = position_dodge(width = .5), vjust = .25)



load("../data/Comparison data/hispanic_comparison.rda")
hispanic_representation <- gather(hispanic_representation, key = "Department", value = representation, c(1:6)) %>% 
  filter(group == "both sexes") %>% 
  filter(area == "Baseline Representation" | area == "Current Representation") %>% 
  select(-1)
hispanic_representation$group <- "Hispanic"
hispanic_representation$width <- ifelse(hispanic_representation$area == "Baseline Representation", 0.7, 0.3)

plot <- hispanic_representation %>% 
  ggplot() +
  geom_bar(aes(Department, representation, fill = area),
           width = hispanic_representation$width,
           position = "dodge",
           stat = "identity") + 
  scale_fill_manual(values = c("#339966", "#33CCCC")) +
  xlab("Company Department") +
  ylab("Representation") + theme(axis.text.x = element_text(angle = 90)) +
  ggtitle("Comparing Company's Representation of Hispanic to Talent Pool") 

plot + geom_text(aes(x = Department, y = representation, label = paste0(100 * round(representation, digits = 4), "%")), 
                 position = position_dodge(width = .5), vjust = .25)



load("../data/Comparison data/multiple_comparison.rda")
multiple_representation <- gather(multiple_representation, key = "Department", value = representation, c(1:6)) %>% 
  filter(group == "both sexes") %>% 
  filter(area == "Baseline Representation" | area == "Current Representation") %>% 
  select(-1)
multiple_representation$group <- "Multiple Races"
multiple_representation$width <- ifelse(multiple_representation$area == "Baseline Representation", 0.7, 0.3)


plot <- multiple_representation %>% 
  ggplot() +
  geom_bar(aes(Department, representation, fill = area),
           width = multiple_representation$width,
           position = "dodge",
           stat = "identity") + 
  scale_fill_manual(values = c("#339966", "#33CCCC")) +
  xlab("Company Department") +
  ylab("Representation") + theme(axis.text.x = element_text(angle = 90)) +
  ggtitle("Comparing Company's Representation of Multiple Races to Talent Pool") 

plot + geom_text(aes(x = Department, y = representation, label = paste0(100 * round(representation, digits = 4), "%")), 
                 position = position_dodge(width = .5), vjust = .25)



load("../data/Comparison data/hawaiian_comparison.rda")
hawaiian_representation <- gather(hawaiian_representation, key = "Department", value = representation, c(1:6)) %>% 
  filter(group == "both sexes") %>% 
  filter(area == "Baseline Representation" | area == "Current Representation") %>% 
  select(-1)
hawaiian_representation$group <- "Native Hawaiian"
hawaiian_representation$width <- ifelse(hawaiian_representation$area == "Baseline Representation", 0.7, 0.3)


plot <- hawaiian_representation %>% 
  ggplot() +
  geom_bar(aes(Department, representation, fill = area),
           width = hawaiian_representation$width,
           position = "dodge",
           stat = "identity") + 
  scale_fill_manual(values = c("#339966", "#33CCCC")) +
  xlab("Company Department") +
  ylab("Representation") + theme(axis.text.x = element_text(angle = 90)) +
  ggtitle("Comparing Company's Representation of Native Hawaiian or Other Pacific Islander to Talent Pool") 

plot + geom_text(aes(x = Department, y = representation, label = paste0(100 * round(representation, digits = 4), "%")), 
                 position = position_dodge(width = .5), vjust = .25)


load("../data/Comparison data/unknown_comparison.rda")
unknown_representation <- gather(unknown_representation, key = "Department", value = representation, c(1:6)) %>% 
  filter(group == "both sexes") %>% 
  filter(area == "Baseline Representation" | area == "Current Representation") %>% 
  select(-1)
unknown_representation$group <- "Unknown"
unknown_representation$width <- ifelse(unknown_representation$area == "Baseline Representation", 0.7, 0.3)


plot <- unknown_representation %>% 
  ggplot() +
  geom_bar(aes(Department, representation, fill = area),
           width = unknown_representation$width,
           position = "dodge",
           stat = "identity") + 
  scale_fill_manual(values = c("#339966", "#33CCCC")) +
  xlab("Company Department") +
  ylab("Representation") + theme(axis.text.x = element_text(angle = 90)) +
  ggtitle("Comparing Company's Representation of Unkown to Talent Pool") 

plot + geom_text(aes(x = Department, y = representation, label = paste0(100 * round(representation, digits = 4), "%")), 
                 position = position_dodge(width = .5), vjust = .25)



load("../data/Comparison data/white_comparison.rda")
white_representation <- gather(white_representation, key = "Department", value = representation, c(1:6)) %>%
  filter(group == "both sexes") %>%
  filter(area == "Baseline Representation" | area == "Current Representation") %>%
  select(-1)
white_representation$group <- "White"
white_representation$width <- ifelse(white_representation$area == "Baseline Representation", 0.7, 0.3)




plot <- white_representation %>% 
  ggplot() +
  geom_bar(aes(Department, representation, fill = area),
           width = white_representation$width,
           position = "dodge",
           stat = "identity") + 
  scale_fill_manual(values = c("#339966", "#33CCCC")) +
  xlab("Company Department") +
  ylab("Representation") + theme(axis.text.x = element_text(angle = 90)) +
  ggtitle("Comparing Company's Representation of White to Talent Pool") 

plot + geom_text(aes(x = Department, y = representation, label = paste0(100 * round(representation, digits = 4), "%")), 
                 position = position_dodge(width = .5), vjust = .25)
```


## Comparing Company's Current Representation of Distinct Ethnic Groups Filtered by Women with the Representation seen in the Talent Pool
```{r, echo = FALSE}
load("../data/Comparison data/ai_an_comparison.rda")
ai_an_representation <- gather(ai_an_representation, key = "Department", value = representation, c(1:6)) %>% 
  filter(group == "women") %>% 
  filter(area == "Baseline Representation" | area == "Current Representation") %>% 
  select(-1)
ai_an_representation$group <- "American Indian"
ai_an_representation$width <- ifelse(ai_an_representation$area == "Baseline Representation", 0.7, 0.3)

plot <- ai_an_representation %>% 
  ggplot() +
  geom_bar(aes(Department, representation, fill = area),
           width = ai_an_representation$width,
           position = "dodge",
           stat = "identity") + 
  scale_fill_manual(values = c("#339966", "#33CCCC")) +
  xlab("Company Department") +
  ylab("Representation") + theme(axis.text.x = element_text(angle = 90)) +
  ggtitle("Comparing Company's Representation of American Indian or Alaskka Native to Talent Pool") 

plot + geom_text(aes(x = Department, y = representation, label = paste0(100 * round(representation, digits = 4), "%")), 
                 position = position_dodge(width = .5), vjust = .25)

load("../data/Comparison data/asian_comparison.rda")
asian_representation <- gather(asian_representation, key = "Department", value = representation, c(1:6)) %>% 
  filter(group == "women") %>% 
  filter(area == "Baseline Representation" | area == "Current Representation") %>% 
  select(-1)
asian_representation$group <- "Asian"
asian_representation$width <- ifelse(asian_representation$area == "Baseline Representation", 0.7, 0.3)


plot <- asian_representation %>% 
  ggplot() +
  geom_bar(aes(Department, representation, fill = area),
           width = asian_representation$width,
           position = "dodge",
           stat = "identity") + 
  scale_fill_manual(values = c("#339966", "#33CCCC")) +
  xlab("Company Department") +
  ylab("Representation") + theme(axis.text.x = element_text(angle = 90)) +
  ggtitle("Comparing Company's Representation of Asian to Talent Pool") 

plot + geom_text(aes(x = Department, y = representation, label = paste0(100 * round(representation, digits = 4), "%")), 
                 position = position_dodge(width = .5), vjust = .25)


load("../data/Comparison data/black_comparison.rda")
black_representation <- gather(black_representation, key = "Department", value = representation, c(1:6)) %>% 
  filter(group == "women") %>% 
  filter(area == "Baseline Representation" | area == "Current Representation") %>% 
  select(-1)
black_representation$group <- "Black"
black_representation$width <- ifelse(black_representation$area == "Baseline Representation", 0.7, 0.3)



plot <- black_representation %>% 
  ggplot() +
  geom_bar(aes(Department, representation, fill = area),
           width = black_representation$width,
           position = "dodge",
           stat = "identity") + 
  scale_fill_manual(values = c("#339966", "#33CCCC")) +
  xlab("Company Department") +
  ylab("Representation") + theme(axis.text.x = element_text(angle = 90)) +
  ggtitle("Comparing Company's Representation of Black to Talent Pool") 

plot + geom_text(aes(x = Department, y = representation, label = paste0(100 * round(representation, digits = 4), "%")), 
                 position = position_dodge(width = .5), vjust = .25)



load("../data/Comparison data/hispanic_comparison.rda")
hispanic_representation <- gather(hispanic_representation, key = "Department", value = representation, c(1:6)) %>% 
  filter(group == "women") %>% 
  filter(area == "Baseline Representation" | area == "Current Representation") %>% 
  select(-1)
hispanic_representation$group <- "Hispanic"
hispanic_representation$width <- ifelse(hispanic_representation$area == "Baseline Representation", 0.7, 0.3)

plot <- hispanic_representation %>% 
  ggplot() +
  geom_bar(aes(Department, representation, fill = area),
           width = hispanic_representation$width,
           position = "dodge",
           stat = "identity") + 
  scale_fill_manual(values = c("#339966", "#33CCCC")) +
  xlab("Company Department") +
  ylab("Representation") + theme(axis.text.x = element_text(angle = 90)) +
  ggtitle("Comparing Company's Representation of Hispanic to Talent Pool") 

plot + geom_text(aes(x = Department, y = representation, label = paste0(100 * round(representation, digits = 4), "%")), 
                 position = position_dodge(width = .5), vjust = .25)



load("../data/Comparison data/multiple_comparison.rda")
multiple_representation <- gather(multiple_representation, key = "Department", value = representation, c(1:6)) %>% 
  filter(group == "women") %>% 
  filter(area == "Baseline Representation" | area == "Current Representation") %>% 
  select(-1)
multiple_representation$group <- "Multiple Races"
multiple_representation$width <- ifelse(multiple_representation$area == "Baseline Representation", 0.7, 0.3)


plot <- multiple_representation %>% 
  ggplot() +
  geom_bar(aes(Department, representation, fill = area),
           width = multiple_representation$width,
           position = "dodge",
           stat = "identity") + 
  scale_fill_manual(values = c("#339966", "#33CCCC")) +
  xlab("Company Department") +
  ylab("Representation") + theme(axis.text.x = element_text(angle = 90)) +
  ggtitle("Comparing Company's Representation of Multiple Races to Talent Pool") 

plot + geom_text(aes(x = Department, y = representation, label = paste0(100 * round(representation, digits = 4), "%")), 
                 position = position_dodge(width = .5), vjust = .25)



load("../data/Comparison data/hawaiian_comparison.rda")
hawaiian_representation <- gather(hawaiian_representation, key = "Department", value = representation, c(1:6)) %>% 
  filter(group == "women") %>% 
  filter(area == "Baseline Representation" | area == "Current Representation") %>% 
  select(-1)
hawaiian_representation$group <- "Native Hawaiian"
hawaiian_representation$width <- ifelse(hawaiian_representation$area == "Baseline Representation", 0.7, 0.3)


plot <- hawaiian_representation %>% 
  ggplot() +
  geom_bar(aes(Department, representation, fill = area),
           width = hawaiian_representation$width,
           position = "dodge",
           stat = "identity") + 
  scale_fill_manual(values = c("#339966", "#33CCCC")) +
  xlab("Company Department") +
  ylab("Representation") + theme(axis.text.x = element_text(angle = 90)) +
  ggtitle("Comparing Company's Representation of Native Hawaiian or Other Pacific Islander to Talent Pool") 

plot + geom_text(aes(x = Department, y = representation, label = paste0(100 * round(representation, digits = 4), "%")), 
                 position = position_dodge(width = .5), vjust = .25)


load("../data/Comparison data/unknown_comparison.rda")
unknown_representation <- gather(unknown_representation, key = "Department", value = representation, c(1:6)) %>% 
  filter(group == "women") %>% 
  filter(area == "Baseline Representation" | area == "Current Representation") %>% 
  select(-1)
unknown_representation$group <- "Unknown"
unknown_representation$width <- ifelse(unknown_representation$area == "Baseline Representation", 0.7, 0.3)


plot <- unknown_representation %>% 
  ggplot() +
  geom_bar(aes(Department, representation, fill = area),
           width = unknown_representation$width,
           position = "dodge",
           stat = "identity") + 
  scale_fill_manual(values = c("#339966", "#33CCCC")) +
  xlab("Company Department") +
  ylab("Representation") + theme(axis.text.x = element_text(angle = 90)) +
  ggtitle("Comparing Company's Representation of Unkown to Talent Pool") 

plot + geom_text(aes(x = Department, y = representation, label = paste0(100 * round(representation, digits = 4), "%")), 
                 position = position_dodge(width = .5), vjust = .25)



load("../data/Comparison data/white_comparison.rda")
white_representation <- gather(white_representation, key = "Department", value = representation, c(1:6)) %>%
  filter(group == "women") %>%
  filter(area == "Baseline Representation" | area == "Current Representation") %>%
  select(-1)
white_representation$group <- "White"
white_representation$width <- ifelse(white_representation$area == "Baseline Representation", 0.7, 0.3)




plot <- white_representation %>% 
  ggplot() +
  geom_bar(aes(Department, representation, fill = area),
           width = white_representation$width,
           position = "dodge",
           stat = "identity") + 
  scale_fill_manual(values = c("#339966", "#33CCCC")) +
  xlab("Company Department") +
  ylab("Representation") + theme(axis.text.x = element_text(angle = 90)) +
  ggtitle("Comparing Company's Representation of White to Talent Pool") 

plot + geom_text(aes(x = Department, y = representation, label = paste0(100 * round(representation, digits = 4), "%")), 
                 position = position_dodge(width = .5), vjust = .25)
```

## Comparing Company's Current Representation of Distinct Ethnic Groups Filtered by Men with the Representation seen in the Talent Pool
```{r, echo = FALSE}
load("../data/Comparison data/ai_an_comparison.rda")
ai_an_representation <- gather(ai_an_representation, key = "Department", value = representation, c(1:6)) %>% 
  filter(group == "men") %>% 
  filter(area == "Baseline Representation" | area == "Current Representation") %>% 
  select(-1)
ai_an_representation$group <- "American Indian"
ai_an_representation$width <- ifelse(ai_an_representation$area == "Baseline Representation", 0.7, 0.3)

plot <- ai_an_representation %>% 
  ggplot() +
  geom_bar(aes(Department, representation, fill = area),
           width = ai_an_representation$width,
           position = "dodge",
           stat = "identity") + 
  scale_fill_manual(values = c("#339966", "#33CCCC")) +
  xlab("Company Department") +
  ylab("Representation") + theme(axis.text.x = element_text(angle = 90)) +
  ggtitle("Comparing Company's Representation of American Indian or Alaskka Native to Talent Pool") 

plot + geom_text(aes(x = Department, y = representation, label = paste0(100 * round(representation, digits = 4), "%")), 
                 position = position_dodge(width = .5), vjust = .25)

load("../data/Comparison data/asian_comparison.rda")
asian_representation <- gather(asian_representation, key = "Department", value = representation, c(1:6)) %>% 
  filter(group == "men") %>% 
  filter(area == "Baseline Representation" | area == "Current Representation") %>% 
  select(-1)
asian_representation$group <- "Asian"
asian_representation$width <- ifelse(asian_representation$area == "Baseline Representation", 0.7, 0.3)


plot <- asian_representation %>% 
  ggplot() +
  geom_bar(aes(Department, representation, fill = area),
           width = asian_representation$width,
           position = "dodge",
           stat = "identity") + 
  scale_fill_manual(values = c("#339966", "#33CCCC")) +
  xlab("Company Department") +
  ylab("Representation") + theme(axis.text.x = element_text(angle = 90)) +
  ggtitle("Comparing Company's Representation of Asian to Talent Pool") 

plot + geom_text(aes(x = Department, y = representation, label = paste0(100 * round(representation, digits = 4), "%")), 
                 position = position_dodge(width = .5), vjust = .25)


load("../data/Comparison data/black_comparison.rda")
black_representation <- gather(black_representation, key = "Department", value = representation, c(1:6)) %>% 
  filter(group == "men") %>% 
  filter(area == "Baseline Representation" | area == "Current Representation") %>% 
  select(-1)
black_representation$group <- "Black"
black_representation$width <- ifelse(black_representation$area == "Baseline Representation", 0.7, 0.3)



plot <- black_representation %>% 
  ggplot() +
  geom_bar(aes(Department, representation, fill = area),
           width = black_representation$width,
           position = "dodge",
           stat = "identity") + 
  scale_fill_manual(values = c("#339966", "#33CCCC")) +
  xlab("Company Department") +
  ylab("Representation") + theme(axis.text.x = element_text(angle = 90)) +
  ggtitle("Comparing Company's Representation of Black to Talent Pool") 

plot + geom_text(aes(x = Department, y = representation, label = paste0(100 * round(representation, digits = 4), "%")), 
                 position = position_dodge(width = .5), vjust = .25)



load("../data/Comparison data/hispanic_comparison.rda")
hispanic_representation <- gather(hispanic_representation, key = "Department", value = representation, c(1:6)) %>% 
  filter(group == "men") %>% 
  filter(area == "Baseline Representation" | area == "Current Representation") %>% 
  select(-1)
hispanic_representation$group <- "Hispanic"
hispanic_representation$width <- ifelse(hispanic_representation$area == "Baseline Representation", 0.7, 0.3)

plot <- hispanic_representation %>% 
  ggplot() +
  geom_bar(aes(Department, representation, fill = area),
           width = hispanic_representation$width,
           position = "dodge",
           stat = "identity") + 
  scale_fill_manual(values = c("#339966", "#33CCCC")) +
  xlab("Company Department") +
  ylab("Representation") + theme(axis.text.x = element_text(angle = 90)) +
  ggtitle("Comparing Company's Representation of Hispanic to Talent Pool") 

plot + geom_text(aes(x = Department, y = representation, label = paste0(100 * round(representation, digits = 4), "%")), 
                 position = position_dodge(width = .5), vjust = .25)



load("../data/Comparison data/multiple_comparison.rda")
multiple_representation <- gather(multiple_representation, key = "Department", value = representation, c(1:6)) %>% 
  filter(group == "men") %>% 
  filter(area == "Baseline Representation" | area == "Current Representation") %>% 
  select(-1)
multiple_representation$group <- "Multiple Races"
multiple_representation$width <- ifelse(multiple_representation$area == "Baseline Representation", 0.7, 0.3)


plot <- multiple_representation %>% 
  ggplot() +
  geom_bar(aes(Department, representation, fill = area),
           width = multiple_representation$width,
           position = "dodge",
           stat = "identity") + 
  scale_fill_manual(values = c("#339966", "#33CCCC")) +
  xlab("Company Department") +
  ylab("Representation") + theme(axis.text.x = element_text(angle = 90)) +
  ggtitle("Comparing Company's Representation of Multiple Races to Talent Pool") 

plot + geom_text(aes(x = Department, y = representation, label = paste0(100 * round(representation, digits = 4), "%")), 
                 position = position_dodge(width = .5), vjust = .25)



load("../data/Comparison data/hawaiian_comparison.rda")
hawaiian_representation <- gather(hawaiian_representation, key = "Department", value = representation, c(1:6)) %>% 
  filter(group == "men") %>% 
  filter(area == "Baseline Representation" | area == "Current Representation") %>% 
  select(-1)
hawaiian_representation$group <- "Native Hawaiian"
hawaiian_representation$width <- ifelse(hawaiian_representation$area == "Baseline Representation", 0.7, 0.3)


plot <- hawaiian_representation %>% 
  ggplot() +
  geom_bar(aes(Department, representation, fill = area),
           width = hawaiian_representation$width,
           position = "dodge",
           stat = "identity") + 
  scale_fill_manual(values = c("#339966", "#33CCCC")) +
  xlab("Company Department") +
  ylab("Representation") + theme(axis.text.x = element_text(angle = 90)) +
  ggtitle("Comparing Company's Representation of Native Hawaiian or Other Pacific Islander to Talent Pool") 

plot + geom_text(aes(x = Department, y = representation, label = paste0(100 * round(representation, digits = 4), "%")), 
                 position = position_dodge(width = .5), vjust = .25)


load("../data/Comparison data/unknown_comparison.rda")
unknown_representation <- gather(unknown_representation, key = "Department", value = representation, c(1:6)) %>% 
  filter(group == "men") %>% 
  filter(area == "Baseline Representation" | area == "Current Representation") %>% 
  select(-1)
unknown_representation$group <- "Unknown"
unknown_representation$width <- ifelse(unknown_representation$area == "Baseline Representation", 0.7, 0.3)


plot <- unknown_representation %>% 
  ggplot() +
  geom_bar(aes(Department, representation, fill = area),
           width = unknown_representation$width,
           position = "dodge",
           stat = "identity") + 
  scale_fill_manual(values = c("#339966", "#33CCCC")) +
  xlab("Company Department") +
  ylab("Representation") + theme(axis.text.x = element_text(angle = 90)) +
  ggtitle("Comparing Company's Representation of Unkown to Talent Pool") 

plot + geom_text(aes(x = Department, y = representation, label = paste0(100 * round(representation, digits = 4), "%")), 
                 position = position_dodge(width = .5), vjust = .25)



load("../data/Comparison data/white_comparison.rda")
white_representation <- gather(white_representation, key = "Department", value = representation, c(1:6)) %>%
  filter(group == "men") %>%
  filter(area == "Baseline Representation" | area == "Current Representation") %>%
  select(-1)
white_representation$group <- "White"
white_representation$width <- ifelse(white_representation$area == "Baseline Representation", 0.7, 0.3)




plot <- white_representation %>% 
  ggplot() +
  geom_bar(aes(Department, representation, fill = area),
           width = white_representation$width,
           position = "dodge",
           stat = "identity") + 
  scale_fill_manual(values = c("#339966", "#33CCCC")) +
  xlab("Company Department") +
  ylab("Representation") + theme(axis.text.x = element_text(angle = 90)) +
  ggtitle("Comparing Company's Representation of White to Talent Pool") 

plot + geom_text(aes(x = Department, y = representation, label = paste0(100 * round(representation, digits = 4), "%")), 
                 position = position_dodge(width = .5), vjust = .25)
```

